A Distributed Mechanism for Intelligent \\ Web Service Community Formation

### 2014-12-02 papers/webservice-coalition-learning/webservice_coalition_learning.tex
cchanges

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{DLISA: Distributed Learning-based \\ Intelligent Service Agents}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%
%
%\IEEEcompsocitemizethanks is a special \thanks that produces the bulleted
% lists the Computer Society journals use for "first footnote" author
% affiliations. Use \IEEEcompsocthanksitem which works much like \item
% for each affiliation group. When not in compsoc mode,
% \IEEEcompsocitemizethanks becomes like \thanks and
% \IEEEcompsocthanksitem becomes a line break with idention. This
% facilitates dual compilation, although admittedly the differences in the
% desired content of \author between the different types of papers makes a
% one-size-fits-all approach a daunting prospect. For instance, compsoc
% journal papers have the author affiliations above the "Manuscript
% received ..."  text while in non-compsoc journals this is reversed. Sigh.

@@

In recent work communities of web services have been proposed that facilitate discovery of web services, improve the Quality of Service (QoS), and help individual services find better market share and opportunities. However, there is a twofold challenge that has still not been addressed. The first challenge is community development, which involves finding the right web services for the community, satisfying all web services and community coordinators involved within the community; and the second challenge is from the individual web service's side , such that a web service seeks communities from which to obtain the best outcome. A number of proposals have attempted to address these research problems. These solutions suffer from two main issues: 
\begin{enumerate}
	\item The solutions consider a centralized manager for communities and most of the decision making process for communities happens at a centralized entity. The problem is in real world scenarios most service providers work in distributed settings and having a centralized entity making decisions is not very feasible. 
	\item The solutions propose complex algorithms \cite{DBLP:conf/IEEEscc/LimTMB12, 10.1109/TSC.2012.12, 10.1109/TSC.2014.2312940} to find the optimal strategy, for each time services or communities adopt an strategy. Or the problem is reduced by eliminating important parameters.
\end{enumerate}
Some of these works propose complex on-demand algorithms \cite{DBLP:conf/IEEEscc/LimTMB12, 10.1109/TSC.2012.12, 10.1109/TSC.2014.2312940} to effectively find target points, but they have to simplify the algorithm with limited parameters in order to make it feasible and algorithm executable. Simplified problems sometimes negatively influence the outcome because simplifying the constraints may cause important aspects of the problem to be ignored. For example, \cite{10.1109/TSC.2012.12} proposes a simple egalitarian way of distributing gain, which completely ignores gain for collaborative work of sub-communities instead of calculating the complex shapely-value gain distribution method. This model considers gain for all subsets of agents working together, which basically ignores the most important criteria of finding the optimal group. Other categories of related work exist that do not focus on all the parties involved within the community \cite{DBLP:conf/IEEEscc/KhosravifarABT11}. 
%And some other work which do not focus on rationality on web services or communities involved [refrences]. 
These solutions generally suffer from high complexity, which makes decision making impossible in an on-demand fashion, or they simplify important aspects to make it practical in the real world, thereby hurting the decision making performance.

@@

The rest of the paper is organized as follows. In Section 2 we briefly describe the preliminaries, discusses the web service community architecture, and the considered parameters in our feature vectors. Section 3 presents our solution model, the way data is trained and web services utilize them in their decision making process. Section 4 describes our experiments and results. Section 5 discussed relevant related work. Finally Section 6, concludes the paper and identifies future work.

@@

\section{Preliminaries}\label{s:preliminaries}
In this section, we first present the architecture of DLISA. We explore the characterestics of intelligent service agents and the features we extract for training. To do this, we first discuss some preliminaries.

>>>>

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{A Distributed Mechanism for Intelligent \\ Web Service Community Formation}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%
%
%\IEEEcompsocitemizethanks is a special \thanks that produces the bulleted
% lists the Computer Society journals use for "first footnote" author
% affiliations. Use \IEEEcompsocthanksitem which works much like \item
% for each affiliation group. When not in compsoc mode,
% \IEEEcompsocitemizethanks becomes like \thanks and
% \IEEEcompsocthanksitem becomes a line break with idention. This
% facilitates dual compilation, although admittedly the differences in the
% desired content of \author between the different types of papers makes a
% one-size-fits-all approach a daunting prospect. For instance, compsoc
% journal papers have the author affiliations above the "Manuscript
% received ..."  text while in non-compsoc journals this is reversed. Sigh.

@@

In recent work communities of web services have been proposed that facilitate discovery of web services, improve the Quality of Service (QoS), and help individual services find better market share and opportunities. However, there is a twofold challenge that has still not been addressed. The first challenge is community development, which involves finding the right web services for the community, satisfying all web services and community coordinators involved within the community; and the second challenge is from the individual web service's side , such that a web service seeks communities from which to obtain the best outcome. A number of proposals have attempted to address these research problems. These solutions suffer from two main issues: 
\begin{enumerate}
	\item The solutions consider a centralized manager for communities and most of the decision making process for communities happens at a centralized entity. The problem is in real world scenarios most service providers work in distributed settings and having a centralized entity making decisions is not very feasible. 
	\item The solutions propose complex algorithms \cite{DBLP:conf/IEEEscc/LimTMB12, 10.1109/TSC.2012.12, 10.1109/TSC.2014.2312940} to find the optimal strategy, for \emph{each time} services or communities adopt an strategy. Or the problem is reduced by eliminating important parameters.
\end{enumerate}
Some of these works propose complex on-demand algorithms \cite{DBLP:conf/IEEEscc/LimTMB12, 10.1109/TSC.2012.12, 10.1109/TSC.2014.2312940} to effectively find target points, but they have to simplify the algorithm with limited parameters in order to make it feasible and algorithm executable. Simplified problems sometimes negatively influence the outcome because simplifying the constraints may cause important aspects of the problem to be ignored. For example, \cite{10.1109/TSC.2012.12} proposes a simple egalitarian way of distributing gain, which completely ignores gain for collaborative work of sub-communities instead of calculating the complex shapely-value gain distribution method. This model considers gain for all subsets of agents working together, which basically ignores the most important criteria of finding the optimal group. Other categories of related work exist that do not focus on all the parties involved within the community \cite{DBLP:conf/IEEEscc/KhosravifarABT11}. 
%And some other work which do not focus on rationality on web services or communities involved [refrences]. 
These solutions generally suffer from high complexity, which makes decision making impossible in an on-demand fashion, or they simplify important aspects to make it practical in the real world, thereby hurting the decision making performance.

@@

The rest of the paper is organized as follows. In Section 2 we briefly describe the preliminaries and problem statement, discusses the web service community architecture, and the considered parameters in our feature vectors. Section 3 presents our solution model, the way data is trained and web services utilize them in their decision making process. Section 4 describes our experiments and results. Section 5 discussed relevant related work. Finally Section 6, concludes the paper and identifies future work.

@@

\section{Preliminaries and Problem Statement}\label{s:preliminaries}
In this section, we first present the architecture of DLISA. We explore the characterestics of intelligent service agents and the features we extract for training. To do this, we first discuss some preliminaries.
